### 2019-02-15 manuscript/methods.tex
done editing Methods

To investigate the association between ploidy level and diversification, we first defined a binary state speciation and extinction model (BiSSE, \citealt{maddison_2007}) in which taxa were classified as diploid (D) or polyploid (P) (\cref{figure:stateclassifications}).
We call this the $D/P$ ploidy model. 
In a Bayesian framework, we obtained posterior probability distributions of speciation rates ($\lambda_D$, $\lambda_P$), extinction rates ($\mu_D$, $\mu_P$), net diversification rates ($r_D=\lambda_D-\mu_D$, $r_P=\lambda_P-\mu_P$), and relative extinction rates ($\nu_D=\mu_D / \lambda_D$, $\nu_D=\mu_D / \lambda_D$) associated with each state.
This analysis explores the same question as \citet{mayrose_2011, mayrose_2015}, but our analyses differ because we include not only polyploidization (parameter $\rho$, the transition rate from $D$ to $P$), but also diploidization (parameter $\delta$, the transition rate from $P$ to $D$). % E: presumably the motivation will be explained in the Intro

Our second model assesses the the signal of diversification due to ploidy while also parsing out the heterogeneity of diversification rates due a possible unobserved trait.
BiSSE-like models can suffer from a large false discovery rate because they fail to account for diversification rate changes that do not directly depend on the trait of interest \citep{rabosky_2015, beaulieu_2016}.
To allow for diversification rate differences explained by something other than ploidy, we added a hidden state (HiSSE model; \citealt{beaulieu_2016}).
In this model, each of the observed diploid and polyploid states is subdivided by a binary hidden trait with states $A$ and $B$.
We call this the $D/P-A/B$ ploidy and hidden state model. 
We estimated the posterior probability distributions of speciation rates ($\lambda_{D_A},\ \lambda_{D_B},\ \lambda_{P_A},\ \lambda_{P_B}$), extinction rates ($\mu_{D_A},\ \mu_{D_B},\ \mu_{P_A},\ \mu_{P_B}$), net diversification rates ($r_{D_A},\ r_{D_B},\ r_{P_A},\ r_{P_B}$), and relative extinction rates ($\nu_{D_A},\ \nu_{D_B},\ \nu_{P_A},\ \nu_{P_B}$).
In this model polyploidization rate $\rho$ and diploidization rate $\delta$ are also included, and changes between hidden states are symmetrical with rate $\alpha$.

@@

To assess the effects of breeding system in the diversification process, we first fit model in which the states are self-incompatible (I) or self-compatible (C).
This is the same as the analysis of \citet{goldberg_2010}, though with an updated phylogeny \citep{sarkinen_2013}.
We call this BiSSE model the $I/C$ breeding system model. 
To parse out the effect of breeding system in diversification while allowing for the possibility of heterogeneous diversification rates unrelated to breeding system, we subdivided each of those states into hidden states $A$ and $B$.
We call this HiSSE model the $I/C-A/B$ breeding system and hidden state model.

@@

If both ploidy and breeding system have the potential to influence lineage diversification, we should logically consider their effects jointly.
We thus fit a model that includes both traits \citep[MuSSE,][]{fitzjohn_2012}.
The three states in this model are self-incompatible diploids (ID), self-compatible diploids (CD), and polyploids, which are always self-compatible (CP).
We did not include a state for self-incompatible polyploids because they are not present in the data, and because that trait combination is logically expected not to occur (as explained above).
We call this the $ID/CD/CP$ ploidy and breeding system model.
It has ten parameters, six for diversification in each state ($\lambda_{ID},\ \lambda_{CD},\ \lambda_{CP}$ for speciation, $\mu_{ID},\ \mu_{CD},\ \mu_{CP}$ for extinction) and four for transitions between states ($\rho_I,\ \rho_C$ for polyploidization transitions from $ID$ and $CD$ to $CP$, respectively; $\delta$ for diploidization from $CP$ to $CD$; $q_{IC}$ for loss of self-incompatibility without polyploidization, from $ID$ to $CD$).
The total rate of loss of self-incompatibility, \ie transitions out of $ID$, is $q_{IC} + \rho_I$.
Diploidization from $CP$ to $ID$ is not allowed because it would be a regain of self-incompatibility.

The $ID/CD/CP$ model could potentially capture similar dynamics as earlier models, if the hidden state in $D/P-A/B$ was effectively breeding system, and the hidden state in $I/C-A/B$ was effectively ploidy.
There is also the potential, however, for a hidden factor to be influencing diversification even beyond both of our focal traits, and this could again mislead inferences.
We therefore added a hidden trait layer on top of our three-state model \citep[analogous to][]{caetano_2018, herrera_2018, huang_2018}.
We refer to this as the $ID/CD/CP-A/B$ model.
A fully parameterized version of this model would have 26 rate parameters \citep{herrera_2018}. 
Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fitted a simplified version with 16 parameters.
The reduction in parameter space is achieved by fixing the rates for transitions among hidden states to be equal with rate $\alpha$, and fixing the transition rates between observed states to be independent of the hidden state (rates $\rho_I,\ \rho_C,\ \delta,\ q_{IC}$ as defined for the $ID/CD/CP$ model).
There are additionally twelve diversification rate parameters ($\lambda_{ID_A},\ \lambda_{ID_B},\ \lambda_{CD_A},\ \lambda_{CD_B},\ \lambda_{CP_A},\ \lambda_{CP_B},\ \mu_{ID_A},\ \mu_{ID_B},\ \mu_{CD_A},\ \mu_{CD_B},\ \mu_{CP_A},\ \mu_{CP_B}$).

@@

For all the four models that consider ploidy changes we assumed that diploidization could happen. Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like ChromEvol \citep{mayrose_2010}. These types of classifications do not allow for a ploidy reversion. Where indicated, the classification of ploidy for the data used in our models was based on chromosome multiplicity at the genus level. However, the majority of the ploidy classifications were adopted from original studies with alternative sources of information (i.e. geographic distribution, genus ploidy distribution) where ploidy was defined by authors that found evidence for it. Since it is not clear whether diploidization can be detected under alternative ploidy classifications or even classifications based on chromosome number multiplicity at the genus level, we also fitted the models without diploidization in order to test  whether including an assumption of diploidization is sensitive. As discussed by \citet{servedio_2014}  the presence or absence of a hypothesis can have an exploratory goal. In our case the diploidization parameter (or the lack of denoted by no $\delta$) in our models  is an opportunity to explore an assumption that might be important but it is not the single definitive process to understand the interactions among polyploidy, breeding system, and diversification.

@@

Parameters for each of the ten diversification models described previously were performed using custom code in RevBayes \citep{hoehna_2016} environment. Code and results for all analyses is freely available at https://github.com/roszenil/solploidy . For all analyses, a correction for sampling bias is included assuming that Solanaceae family has approximately 3,000 species ($s=595/3000$) as estimated by the Solanaceae Source project \citep{solsource}. For all ten models, we assumed that speciation and extinction parameters for all models  had log-normal prior distributions with means equal the expected net diversification rate $ ( \frac{(\textrm{number of taxa})/2}{\textrm{root age}})$ and standard deviation $0.5$.
Prior distributions for parameters defining trait changes were  assumed to be gamma distributed with parameters $k=0.5$ and $\theta=1$. 
For each model, an MCMC was performed for 96 hours in the high-performance computational cluster at Minnesota Supercomputing Institute which allowed for 5,000 generation of burn-in and a minimum of 200,000 generations of MCMC for each of the 6 models. For each model, convergence and mixing of the MCMC was tested using R package coda and software Tracer (see supplementary information for convergence plots).

@@

We calculated the marginal likelihoods  for each of the ten models using custom code in RevBayes \citet{hoehna_2016}.  Marginal likelihoods were calculated using 50  stepping stone steps using the methodology of \citet{xie_2010}. Each stepping stone step was found by calculating 500 generations of burn-in followed by a total of 1000 MCMC steps \cref{table:marginallike}.  The calculation of each marginal likelihood ran for 24 hours in the high-performance computational cluster at Minnesota Supercomputing Institute.\newline

Using the marginal likelihood values we calculated fourteen different Bayes factors in log-scale. The first six Bayes factors compared the four models of polyploidy against each other, followed by one single comparison between the breeding system models, and finalizing with four comparisons between each polyploidy and breeding system models (see \cref{table:bayesfactors} for all comparisons). Comparison between polyploidy models vs. polyploidy and breeding system models are not valid for two reasons: first, the input data in each model is numerically different (see \cref{table:stateclassifications} for data classifications)
%R: Emma this is where the figure can be important to show that we have to make different input
; second, even when it is possible to re-write the polyploidy and diversification models to include a hidden state that would account for breeding system allowing to use the same input data, the re-written model would still not be comparable to the multivariate SSE models proposed for polyploidy and breeding system due to the hierarchical structure imposed by the interaction between breeding system and polyploidy. This second point has been recently denoted by \citet{tarasov_2019} as the lack of lumpability in Markov models for discrete traits.  In our particular case, polyploids cannot be self compatible, and the irreversibility of self-compatible to self-incompatible state makes the three-state Markov models non-lumpable into two-state models ultimately making  multivariate and the bivariate models incomparable.

%\begin{table}
%\begin{tabular}{@{}llccc@{}} \toprule
%\multicolumn{4}{r}{Models} \\ \cmidrule(r){3-5}
%Type & Total of & D/P and D/P-A/B& I/C and I/C-A/B & ID/P/CD and CD/P/ID-A/B\\ \midrule
%Diploid Self Compatible & 152 & 0 &  0 & 0 \\
%Diploid Self Incompatible& 97 & 0  & 1 & 2\\
%Diploid with unknown breeding system & 219 & 0 & (0,1) & (0,2) \\
%Polyploid & 81 & 1& 0 & 1 \\
%Unknow ploidy and self compatible& 34 & (0,1)& 0 & (0,1) \\ 
%Unknown ploidy and self incompatible & 12 & 0 & 1 & 2 \\ \bottomrule
%\end{tabular}
%\caption{Binary and three state classifications for 595 taxa with ploidy and/or breeding system data. The number of taxa in the the sample was maximized by including tips with only ploidy or only breeding system and assigned them as uncertain in the unknown character.}
% E: but P are not SI
%\label{table:stateclassifications}
%\end{table}

\begin{table}
\begin{tabular}{@{}llcccccc@{}} \toprule
%\multicolumn{4}{r}{Models} \\ \cmidrule(r){3-5}
Model& Model& Ploidy & Diploidization & Breeding  & Hidden & Parameters & Marginal \\
& Type & &  &System & State & & Log- Likelihood \\
1. D/P &BiSSE &	Yes  &	Yes &	No	&No	& 6	& -1182.93 \\
2. D/P no $\delta$ & BiSSE  &	Yes & 	No	& No	& No & 	5 &	-1193.66\\
3. D/P- A/B  & HiSSE &	Yes &	Yes	&No &	Yes &	11 &	\textbf{-1145.69}\\
4. D/P no $\delta$-A/B &	HiSSE &	Yes & No &	No &	Yes &	10	&-1150.99\\
5. I/C &	BiSSE &	No &	 No	&Yes &	No &	 5 &  -1194.80 \\
6. I/C-A/B &	HiSSE &	No &	 No	&Yes &	Yes	& 10 & \textbf{-1155.37}\\
7. ID/P/CD & MuSSE &	Yes & 	Yes &	Yes &	No &	10 & -1344.50\\
8. ID/P/CD no $\delta$ &	MuSSE &	Yes & 	No &	Yes	&No &	9 &-1345.87\\
9. ID/P/CD-A/B & MuHiSSE &	Yes 	&Yes &	Yes &	Yes &	16 & \textbf{-1300.35} \\
10.ID/P/CD no $\delta$-A/B &	 MuHiSSE	 & Yes & 	No	&Yes &	Yes	&15 &-1303.55 \\ \bottomrule
\end{tabular}
\caption{Marginal likelihoods for the ten diversification models proposed.}
% E: but P are not SI
\label{table:marginallike}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|c|c|c|}
\toprule
Polyploidy Models & Breeding System Models & Polyploidy and Breeding System Models \\ \midrule
{\begin{tabular}{lcccc}
 & 1 & 2 & 3 & 4 \\
1. D/P & $\cdot$	 &10.72 &	-37.24	&-31.94\\
2. D/P no $\delta$ &$\cdot$&$\cdot$ &	-47.97	&-42.66\\
\textbf{3. D/P- A/B}  &$\cdot$  & $\cdot$&	$\cdot$	& 5.30 \\
4. D/P no $\delta$-A/B &$\cdot$& $\cdot$ & $\cdot$&$\cdot$ \\
\end{tabular}
}  & 
{\begin{tabular}{lcc}
 & 5 & 6\\
5. I/C &$\cdot$ & -39.43 \\
\textbf{6. I/C-A/B} &$\cdot$& $\cdot$ \\
& & \\
& & \\
\end{tabular}
} & 
{\begin{tabular}{lcccc}
& 7 & 8 & 9 & 10\\
7. ID/P/CD & $\cdot$	&1.36 & -44.15&-40.95 \\
8. ID/P/CD no $\delta$ & $\cdot$ & $\cdot$ & -45.51 &-42.31 \\
\textbf{9. ID/P/CD-A/B}& $\cdot$ & $\cdot$ &$\cdot$	& 3.2 \\ 
10. ID/P/CD no $\delta$-A/B & $\cdot$& $\cdot$&$\cdot$ & $\cdot$\\
\end{tabular}
}\\
\bottomrule
\end{tabular}
 \caption{Bayes factors in log scale. We compare every possible pair. Number models as indicated in  \cref{table:marginallike}. }
% E: but P are not SI
\label{table:bayesfactors}
\end{table}

>>>>

To investigate the association between ploidy level and diversification, we first defined a binary state speciation and extinction model (BiSSE, \citealt{maddison_2007}) in which taxa were classified as diploid (D) or polyploid (P) (\cref{figure:stateclassifications}).
We call this the D/P ploidy model. 
In a Bayesian framework, we obtained posterior probability distributions of speciation rates ($\lambda_D$, $\lambda_P$), extinction rates ($\mu_D$, $\mu_P$), net diversification rates ($r_D=\lambda_D-\mu_D$, $r_P=\lambda_P-\mu_P$), and relative extinction rates ($\nu_D=\mu_D / \lambda_D$, $\nu_D=\mu_D / \lambda_D$) associated with each state.
This analysis explores the same question as \citet{mayrose_2011, mayrose_2015}, but our analyses differ because we include not only polyploidization (parameter $\rho$, the transition rate from $D$ to $P$), but also diploidization (parameter $\delta$, the transition rate from $P$ to $D$). % E: presumably the motivation will be explained in the Intro

Our second model assesses the the signal of diversification due to ploidy while also parsing out the heterogeneity of diversification rates due a possible unobserved trait.
BiSSE-like models can suffer from a large false discovery rate because they fail to account for diversification rate changes that do not directly depend on the trait of interest \citep{rabosky_2015, beaulieu_2016}.
To allow for diversification rate differences explained by something other than ploidy, we added a hidden state (HiSSE model; \citealt{beaulieu_2016}).
In this model, each of the observed diploid and polyploid states is subdivided by a binary hidden trait with states $A$ and $B$.
We call this the D/P--A/B ploidy and hidden state model. 
We estimated the posterior probability distributions of speciation rates ($\lambda_{D_A},\ \lambda_{D_B},\ \lambda_{P_A},\ \lambda_{P_B}$), extinction rates ($\mu_{D_A},\ \mu_{D_B},\ \mu_{P_A},\ \mu_{P_B}$), net diversification rates ($r_{D_A},\ r_{D_B},\ r_{P_A},\ r_{P_B}$), and relative extinction rates ($\nu_{D_A},\ \nu_{D_B},\ \nu_{P_A},\ \nu_{P_B}$).
In this model polyploidization rate $\rho$ and diploidization rate $\delta$ are also included, and changes between hidden states are symmetrical with rate $\alpha$.

@@

To assess the effects of breeding system in the diversification process, we first fit model in which the states are self-incompatible (I) or self-compatible (C).
This is the same as the analysis of \citet{goldberg_2010}, though with an updated phylogeny \citep{sarkinen_2013}.
We call this BiSSE model the I/C breeding system model. 
To parse out the effect of breeding system in diversification while allowing for the possibility of heterogeneous diversification rates unrelated to breeding system, we subdivided each of those states into hidden states $A$ and $B$.
We call this HiSSE model the I/C--A/B breeding system and hidden state model.

@@

If both ploidy and breeding system have the potential to influence lineage diversification, we should logically consider their effects jointly.
We thus fit a model that includes both traits \citep[MuSSE,][]{fitzjohn_2012}.
The three states in this model are self-incompatible diploids (ID), self-compatible diploids (CD), and polyploids, which are always self-compatible (CP).
We did not include a state for self-incompatible polyploids because they are not present in the data, and because that trait combination is logically expected not to occur (as explained above).
We call this the ID/CD/CP ploidy and breeding system model.
It has ten parameters, six for diversification in each state ($\lambda_{ID},\ \lambda_{CD},\ \lambda_{CP}$ for speciation, $\mu_{ID},\ \mu_{CD},\ \mu_{CP}$ for extinction) and four for transitions between states ($\rho_I,\ \rho_C$ for polyploidization transitions from $ID$ and $CD$ to $CP$, respectively; $\delta$ for diploidization from $CP$ to $CD$; $q_{IC}$ for loss of self-incompatibility without polyploidization, from $ID$ to $CD$).
The total rate of loss of self-incompatibility, \ie transitions out of $ID$, is $q_{IC} + \rho_I$.
Diploidization from $CP$ to $ID$ is not allowed because it would be a regain of self-incompatibility.

The ID/CD/CP model could potentially capture similar dynamics as earlier models, if the hidden state in D/P--A/B was effectively breeding system, and the hidden state in I/C--A/B was effectively ploidy.
There is also the potential, however, for a hidden factor to be influencing diversification even beyond both of our focal traits, and this could again mislead inferences.
We therefore added a hidden trait layer on top of our three-state model \citep[analogous to][]{caetano_2018, herrera_2018, huang_2018}.
We refer to this as the ID/CD/CP--A/B model.
A fully parameterized version of this model would have 26 rate parameters \citep{herrera_2018}. 
Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fitted a simplified version with 16 parameters.
The reduction in parameter space is achieved by fixing the rates for transitions among hidden states to be equal with rate $\alpha$, and fixing the transition rates between observed states to be independent of the hidden state (rates $\rho_I,\ \rho_C,\ \delta,\ q_{IC}$ as defined for the ID/CD/CP model).
There are additionally twelve diversification rate parameters ($\lambda_{ID_A},\ \lambda_{ID_B},\ \lambda_{CD_A},\ \lambda_{CD_B},\ \lambda_{CP_A},\ \lambda_{CP_B},\ \mu_{ID_A},\ \mu_{ID_B},\ \mu_{CD_A},\ \mu_{CD_B},\ \mu_{CP_A},\ \mu_{CP_B}$).

@@

For all four models that consider ploidy changes, we allowed that diploidization could happen.
Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010}.
These types of classifications do not allow for a ploidy reversion.
Where indicated, the classification of ploidy for the data used in our models was based on chromosome multiplicity at the genus level.
% ref data/sources table?
However, the majority of the ploidy classifications were adopted from original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution) where ploidy was defined by authors that found evidence for it.
Since it is not clear whether diploidization can be detected under alternative ploidy classifications or even classifications based on chromosome number multiplicity at the genus level, we also fit the models without diploidization in order to test  whether the conclusions about diversification are sensitive to including diploidization.
As discussed by \citet{servedio_2014}, the presence or absence of a hypothesis can have an exploratory goal.
In our case the diploidization parameter (or its absence, $\delta=0$) in our models is an opportunity to explore an assumption that might be important but that is not the single definitive process to understand the interactions among polyploidy, breeding system, and diversification.

@@

Parameters for each of the ten diversification models were performed using custom code in the RevBayes \citep{hoehna_2016} environment.
Code and results for all analyses is available at \url{https://github.com/roszenil/solploidy}.
For all analyses, a correction for incomplete sampling was included, based on assuming that the Solanaceae family has approximately 3,000 species ($s=595/3000$) as estimated by the Solanaceae Source project \citep{solsource}.
For all ten models, we assumed that speciation and extinction parameters  had log-normal prior distributions with means equal to the expected net diversification rate $(\text{number of taxa} / [2 \times \text{root age}])$ and standard deviation $0.5$.
Priors for parameters defining trait changes were assumed to be gamma distributed with parameters $k=0.5$ and $\theta=1$. 
For each model, an MCMC chain was run for 96 hours in the high-performance computational cluster at Minnesota Supercomputing Institute, which allowed for 5,000 generation of burn-in and a minimum of 200,000 generations of MCMC for each of the 6 models. 
For each model, convergence and mixing of the MCMC was tested using the R package coda and the software Tracer (see supplementary information for convergence plots). % eventually, add supp info fig ref

@@

We calculated the marginal likelihood for each of the ten models in RevBayes \citep{hoehna_2016}.
Marginal likelihoods were calculated using 50 stepping stone steps under the methodology of \citet{xie_2010}.
Each stepping stone step was found by calculating 500 generations of burn-in followed by a total of 1000 MCMC steps (\cref{table:marginallike}).
The calculation of each marginal likelihood ran for 24 hours on a high-performance computational cluster.

Using the marginal likelihood values, we calculated thirteen different Bayes factors. % E: it said "fourteen" but I only count thirteen?
Six compared the models of polyploidy against each other (D/P and D/P--A/B, each with or without diploidization), one compared the breeding system models (I/C and I/C--A/B), and six compared the models with both traits (ID/CD/CP and ID/CD/CP--A/B, each with or without diploidization) (\cref{table:bayesfactors}).
%
Other comparisons between these models are not valid because the input data are different under the different state space codings (\cref{figure:stateclassifications}).
In essence, the D/P, I/C, and ID/CD/CP state spaces are not lumpable with respect to one another \citep{tarasov_2019}.
%R: Emma this is where the figure can be important to show that we have to make different input
% E: I think this short explanation is clear enough, especially with the figure.  I'm not sure whether the hierarchical concept is exactly applicable here.

%\begin{table}
%\begin{tabular}{@{}llccc@{}} \toprule
%\multicolumn{4}{r}{Models} \\ \cmidrule(r){3-5}
%Type & Total of & D/P and D/P-A/B& I/C and I/C-A/B & ID/P/CD and CD/P/ID-A/B\\ \midrule
%Diploid Self Compatible & 152 & 0 &  0 & 0 \\
%Diploid Self Incompatible& 97 & 0  & 1 & 2\\
%Diploid with unknown breeding system & 219 & 0 & (0,1) & (0,2) \\
%Polyploid & 81 & 1& 0 & 1 \\
%Unknow ploidy and self compatible& 34 & (0,1)& 0 & (0,1) \\ 
%Unknown ploidy and self incompatible & 12 & 0 & 1 & 2 \\ \bottomrule
%\end{tabular}
%\caption{Binary and three state classifications for 595 taxa with ploidy and/or breeding system data. The number of taxa in the the sample was maximized by including tips with only ploidy or only breeding system and assigned them as uncertain in the unknown character.}
%\label{table:stateclassifications}
%\end{table}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known.
The number of species in each is shown under the corresponding circles in the top row.
These categories were then grouped in a manner appropriate to the states of each model.
For example, there are 34 species that are self-compatible and of unknown ploidy; these are coded as either $D$ or $P$ in the D/P models (uncertain, or consistent with either state), as $C$ in the I/C models, and as either $CD$ or $CP$ in the ID/CD/CP models.
In all cases, species were coded as either $A$ or $B$ in the hidden state models.
}
\label{figure:stateclassifications}
\end{figure}

\begin{table}
\begin{tabular}{@{}llcccccc@{}} \toprule
%\multicolumn{4}{r}{Models} \\ \cmidrule(r){3-5}
Model& Model& Ploidy & Diploidization & Breeding  & Hidden & Parameters & Marginal \\
& Type & &  &System & State & & Log- Likelihood \\
1. D/P &BiSSE &	Yes  &	Yes &	No	&No	& 6	& -1182.93 \\
2. D/P no $\delta$ & BiSSE  &	Yes & 	No	& No	& No & 	5 &	-1193.66\\
3. D/P- A/B  & HiSSE &	Yes &	Yes	&No &	Yes &	11 &	\textbf{-1145.69}\\
4. D/P no $\delta$-A/B &	HiSSE &	Yes & No &	No &	Yes &	10	&-1150.99\\
5. I/C &	BiSSE &	No &	 No	&Yes &	No &	 5 &  -1194.80 \\
6. I/C-A/B &	HiSSE &	No &	 No	&Yes &	Yes	& 10 & \textbf{-1155.37}\\
7. ID/P/CD & MuSSE &	Yes & 	Yes &	Yes &	No &	10 & -1344.50\\
8. ID/P/CD no $\delta$ &	MuSSE &	Yes & 	No &	Yes	&No &	9 &-1345.87\\
9. ID/P/CD-A/B & MuHiSSE &	Yes 	&Yes &	Yes &	Yes &	16 & \textbf{-1300.35} \\
10.ID/P/CD no $\delta$-A/B &	 MuHiSSE	 & Yes & 	No	&Yes &	Yes	&15 &-1303.55 \\ \bottomrule
\end{tabular}
\caption{Marginal likelihoods for the ten diversification models proposed.}
\label{table:marginallike}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|c|c|c|}
\toprule
Polyploidy Models & Breeding System Models & Polyploidy and Breeding System Models \\ \midrule
{\begin{tabular}{lcccc}
 & 1 & 2 & 3 & 4 \\
1. D/P & $\cdot$	 &10.72 &	-37.24	&-31.94\\
2. D/P no $\delta$ &$\cdot$&$\cdot$ &	-47.97	&-42.66\\
\textbf{3. D/P- A/B}  &$\cdot$  & $\cdot$&	$\cdot$	& 5.30 \\
4. D/P no $\delta$-A/B &$\cdot$& $\cdot$ & $\cdot$&$\cdot$ \\
\end{tabular}
}  & 
{\begin{tabular}{lcc}
 & 5 & 6\\
5. I/C &$\cdot$ & -39.43 \\
\textbf{6. I/C-A/B} &$\cdot$& $\cdot$ \\
& & \\
& & \\
\end{tabular}
} & 
{\begin{tabular}{lcccc}
& 7 & 8 & 9 & 10\\
7. ID/P/CD & $\cdot$	&1.36 & -44.15&-40.95 \\
8. ID/P/CD no $\delta$ & $\cdot$ & $\cdot$ & -45.51 &-42.31 \\
\textbf{9. ID/P/CD-A/B}& $\cdot$ & $\cdot$ &$\cdot$	& 3.2 \\ 
10. ID/P/CD no $\delta$-A/B & $\cdot$& $\cdot$&$\cdot$ & $\cdot$\\
\end{tabular}
}\\
\bottomrule
\end{tabular}
 \caption{Bayes factors in log scale. We compare every possible pair. Number models as indicated in  \cref{table:marginallike}. }
\label{table:bayesfactors}
\end{table}
